---
title: "ggcal"
author: "Jay Jacobs"
date: "3/18/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`ggcal` is a simple package to generate a familiar calendar plot from a vector of dates and 
fill values.

## Installation

```{r eval=FALSE}
devtools::install_github("jayjacobs/ggcal")
```

## Generating a simple calendar plot

```{r}
mydate <- seq(as.Date("2017-02-01"), as.Date("2017-07-22"), by="1 day")
myfills <- rnorm(length(mydate))

print(ggcal(mydate, myfills))
```

The function returns as base ggplot object, which can be modified with `scale_fill_*` 

```{r}
gg <- ggcal(mydate, myfills) +
  scale_fill_gradient2(low="#4575b4", mid="#ffffbf", high="#d73027", midpoint=0)

print(gg)
```

Notice how the last few days in July are missing in the original data and are set to a dark gray by default.  This can be overridden in the `scale_fill_*` function.

```{r}
mydate2 <- sample(mydate, 100) 
myfills2 <- rnorm(length(mydate2))

gg <- ggcal(mydate2, myfills2) +
  scale_fill_gradient2(low="#4575b4", mid="#ffffbf", high="#d73027", midpoint=0,
                       na.value="gray95")

print(gg)

```

The fill values also do not have to be a continuous variable.

```{r}
mydate <- seq(as.Date("2017-02-01"), as.Date("2017-07-31"), by="1 day")
myfills <- ifelse(format(mydate, "%w") %in% c(0,6), "weekend" ,"weekday")

ggcal(mydate, myfills) + scale_fill_manual(values=c("weekday"="steelblue", "weekend"="lightsteelblue"))
```

